The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-25 article.tex
Added missing Signature code examples

  An implementation has been provided of the Signature structure descriptor for
  molecules~\cite{Faulon2003}. These act as a linear notation - like the SMILES format - 
  for the whole molecule as well as for connected substructures rooted at a single atom. The 
  descriptor can also be canonicalized to provide isomorphism-independent
  representations~\cite{Faulon2004}. Signatures can be calculated for atoms with:

\begin{verbatim}
\end{verbatim}

@@

\begin{verbatim}
\end{verbatim}

  Finally, a signatures fingerprint can be calculated for molecules, to allow
  similarity calculations. This can then be used in QSAR modeling~\cite{signaturefingerprints,
  Spjuth2011DS,Moghadam2015,Alvarsson2014,Spjuth2012OS,Norinder2013,Alvarsson2016}.
  The fingerprint for a molecule can be calculated with:

\begin{verbatim}
\end{verbatim}

>>>>

  An implementation has been provided of the Signature structure descriptor for
  molecules~\cite{Faulon2003}. These act as a linear notation - like the SMILES format - 
  for the whole molecule as well as for connected substructures rooted at a single atom. The 
  descriptor can also be canonicalized to provide isomorphism-independent
  representations~\cite{Faulon2004}. Signatures of depth two can be calculated
  for atoms with:

\begin{verbatim}
for (IAtom atom : molecule.atoms()) {
  String signature = new AtomSignature(atom, 2, molecule).toCanonicalString();
}
\end{verbatim}

@@

\begin{verbatim}
String signature = new MoleculeSignature(molecule).toCanonicalString();
\end{verbatim}

  Finally, a signatures fingerprint can be calculated for molecules, to allow
  similarity calculations. This can then be used in QSAR modeling~\cite{signaturefingerprints,
  Spjuth2011DS,Moghadam2015,Alvarsson2014,Spjuth2012OS,Norinder2013,Alvarsson2016}.
